---
title: "Alcohol vs Seat choice"
author: "Johana Quintanilla"
date: "Fall 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

The number of people sitting in the back row is the smallest number of people (36). In the middle row is  where most people are sitting (89). In the front row is where less people are sitting than the middle row but more than the back row (40). 

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

When looking at the p value, which was about 0.000116,  I noticed that it is really small and it tells me that there is a statistical difference between the values. 

```{r}
plot(TukeyHSD(model1))
```

Looking at the 95% confidence level, We saw the confidence intervals of the Front-Back, Middle-Back, and Middle-Front seats, with 0 indicating if the lines are significantly different. When we observed the results, the Front-Back and the Middle-Back are indeed significantly different, since 0 doesn't go through the confidence interval. However, for the middle-front seats, 0 does go through the confidence interval, indicating that there is no significant difference between them. 

## Conclusions

What we learned in today's lesson when looking at numerical categorical data, there are different categories. Because of this, we used our helper file labeled "Numerical~Cat-1.rmd".The numerical results showed us the number of people sitting in the front, middle, and back lines, and we were able to see the number of people in each row, with the middle row having the highest number of people with 89 seats.There were Inferential results which provided us with the P-value and it was really small (0.000116). This p-Value said that the results are significantly different, and so we went ahead and plotted a 95% confidence level chart to be able to dive more into the results. We noticed that the Front-Back and the Middle-Back are significantly different, since 0 doesn't go through their confidence intervals. In contrast, for the Middle-Front seats, 0 goes through the confidence interval, and so indicating that there is no significant difference between them.
